\documentclass[pdflatex]{sn-jnl}
 \renewcommand{\textfraction}{.002}
\renewcommand{\floatpagefraction}{.995}
\setcounter{totalnumber}{5}
\renewcommand{\topfraction}{.995}

\usepackage[numbers,square]{natbib}
\bibliographystyle{spbasic_u}

\usepackage[noend,ruled,vlined]{algorithm2e}
\newcommand\mycommfont[1]{\footnotesize\ttfamily{#1}}
\SetCommentSty{mycommfont}


\usepackage{graphicx}%
\usepackage{multirow}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{amsthm}%
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
\usepackage{booktabs}%
\usepackage{placeins}
\usepackage{listings}%
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{xr}
\usepackage{bm}
%% CUSTOM PACKAGES
%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{hyperref}
\usepackage{array}
\usepackage{tabularx}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}
%\usetikzlibrary{3d,perspective}
%\usetikzlibrary{shapes.geometric, arrows.meta, positioning}
\usepackage{booktabs} % For better table lines
\usepackage[version=4]{mhchem} 
\usepackage{enumitem}
\usepackage{algorithm2e}
%\usepackage{arydshln}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% as per the requirement new theorem styles can be included as shown below
\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
\newtheorem{corollary}[theorem]{Corollary}% 
\newtheorem{proposition}[theorem]{Proposition}%
\newtheorem{lemma}[theorem]{Lemma}% 
\newtheorem{conjecture}[theorem]{Conjecture}%
\newtheorem{observation}[theorem]{Observation}%
%
\makeatletter
\newtheoremstyle{examplesty}% Numbered
{18pt plus2pt minus1pt}% Space above
{18pt plus2pt minus1pt}% Space below
{\normalfont}% Body font
{0pt}% Indent amount
{\bfseries}% Theorem head font
{.}% Punctuation after theorem head
{.5em}% Space after theorem headi
{\thmname{#1}\thmnumber{\@ifnotempty{#1}{ }{#2}}%
  \thmnote{ {\the\thm@notefont(#3)}}}% Theorem head spec (can be left empty, meaning `normal')
\makeatother
\theoremstyle{examplesty}%
\newtheorem{example}{Example}%
%\newtheorem{remark}{Remark}%
%
\theoremstyle{thmstylethree}%
\newtheorem{definition}[theorem]{Definition}%

\newenvironment{mainitem}[2]{\medskip\par\noindent%
  \textbf{#1~M\ref{#2}.}}{\par}


%%%%% SOME LOW LEVEL STUFF NEEDED FOR SPECIAL SYMBOLS
\makeatletter
\def\moverlay{\mathpalette\mov@rlay}
\def\mov@rlay#1#2{\leavevmode\vtop{%
    \baselineskip\z@skip \lineskiplimit-\maxdimen
    \ialign{\hfil$\m@th#1##$\hfil\cr#2\crcr}}}
\newcommand{\charfusion}[3][\mathord]{
  #1{\ifx#1\mathop\vphantom{#2}\fi
    \mathpalette\mov@rlay{#2\cr#3}
  }
  \ifx#1\mathop\expandafter\displaylimits\fi}
\DeclareRobustCommand\bigop[1]{%
  \mathop{\vphantom{\sum}\mathpalette\bigop@{#1}}\slimits@
}
\newcommand{\bigop@}[2]{%
  \vcenter{%
    \sbox\z@{$#1\sum$}%
    \hbox{\resizebox{\ifx#1\displaystyle.9\fi\dimexpr\ht\z@+\dp\z@}{!}{$\m@th#2$
}}%
  }%
}
\makeatother
%%%%% END LOWLEVEL USER DEFINITION

\newcommand{\cupdot}{\charfusion[\mathbin]{\cup}{\cdot}}
\DeclareMathOperator{\bigcupdot}{\charfusion[\mathop]{\bigcup}{\cdot}}
% \DeclareMathOperator{\Aut}{Aut}
% \DeclareMathOperator{\orb}{orb}
\newcommand{\whatever}{\mbox{\,.\,}}
\newcommand{\king}{\mathbf{K}}
\newcommand{\queen}{\mathbf{Q}}
\newcommand{\SM}{\mathbf{S}}
\newcommand{\closure}[2]{\mathscr{C}_{#1}(#2)}
\newcommand{\cl}[0]{\mathscr{X}}
\newcommand{\PO}[0]{\mathscr{R}}
\newcommand{\POR}[0]{\mathcal{R}}
\newcommand{\RAF}[0]{\mathbf{R}}
\newcommand{\POX}[0]{\mathcal{X}}
\newcommand{\cat}{\mathcal{K}}
\newcommand{\ORCID}[1]{}
\DeclareMathOperator{\suck}{succ}
\newcommand{\Code}[1]{\texttt{\upshape{#1}}}
\newcommand{\pfad}[0]{\ensuremath{\mathbf{P}}}
\newcommand{\stack}[0]{\ensuremath{\mathbf{T}}}
\newcommand{\child}{\pmb{\kappa}}

\definecolor{middlegreen}{RGB}{0,128,0}
\definecolor{royalpurple}{RGB}{85,26,139}
\newcommand{\NEW}[1]{\begingroup\color{blue}#1\endgroup}
\newcommand{\TODO}[1]{\begingroup\color{red}#1\endgroup}
\newcommand{\PFS}[1]{\begingroup\color{blue}#1\endgroup}
\newcommand{\holy}[1]{\begingroup\color{royalpurple}#1\endgroup}
\newcommand{\TG}[1]{\begingroup\color{green}#1\endgroup}
\newcommand{\NV}[1]{\begingroup\color{teal}#1\endgroup}
\newcommand{\OLD}[1]{\begingroup\tiny\color{gray}#1\endgroup}



% Linenumbers for debugging
\usepackage{lineno}
\linenumbers
\raggedbottom

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{RAF-Cores} 

%% comment: 

\author*[1,4]{\fnm{Richard} \sur{Golnik}}\email{richard@bioinf.uni-leipzig.de}
\ORCID{0000-0002-8582-5006} 
%
%\author[1]{\fnm{Thomas} \sur{Gatter}}\email{thomas@bioinf.uni-leipzig.de}
%\ORCID{0000-0002-5016-5191} 
%
%\author[1,2]{\fnm{Nicola} \sur{Vassena}}\email{nicola.vassena@uni-leipzig.de}
%
%\ORCID{0000-0001-5411-4976} 
%
%\author[1,2,3,4,5,6,7,8,9]{\fnm{Peter F.}\sur{Stadler}}\email{studla@bioinf.uni-leipzig.de}
%\ORCID{0000-0001-5567-3016}


\affil[1]{\orgdiv{Bioinformatics Group, Department of Computer Science}
  \orgname{Leipzig University}, \orgaddress{\street{H{\"a}rtelstra{\ss}e 16–18},
    \postcode{D-04107} \city{Leipzig}, \country{Germany}}}

\affil[2]{\orgdiv{Interdisciplinary Center for Bioinformatics}
	\orgaddress{\orgname{Leipzig University}, \postcode{D-04107}
	 \city{Leipzig}, \country{Germany}}}  
	 
\affil[3]{\orgdiv{Center for Scalabale Data Analytics and Artificial Intelligence},
  \orgaddress{\orgname{Leipzig University}, \postcode{D-04107}
    \city{Leipzig}, \country{Germany}}} 

\affil[4]{\orgdiv{Zuse School for Embedded and Composite Artificial Intelligence (SECAI)}
   \orgaddress{\orgname{Leipzig University}, \postcode{D-04107}
    \city{Leipzig}, \country{Germany}}}

\affil[5]{\orgname{Max Planck Institute for Mathematics in the Sciences},
  \orgaddress{\street{Inselstra{\ss}e 22}, \postcode{D-04103}
    \city{Leipzig}, \country{Germany}}}

\affil[6]{\orgdiv{Department of Theoretical Chemistry}, \orgname{University
    of Vienna}, \orgaddress{\street{W{\"a}hringerstra{\ss}e 17},
    \postcode{A-1090} \city{Wien}, \country{Austria}}}

\affil[7]{\orgdiv{Facultad de Ciencias}, \orgname{Universidad National de
    Colombia}, \orgaddress{\city{Bogot{\'a}}, \country{Colombia}}}

\affil[8]{\orgdiv{Center for non-coding RNA in Technology and Health},
  \orgname{University of Copenhagen}, \orgaddress{\street{Ridebanevej 9},
    \postcode{DK-1870} \city{Frederiksberg}, \country{Denmark}}}

\affil[9]{\orgname{Santa Fe Institute}, \orgaddress{\street{1399 Hyde Park
      Rd.}, \city{Santa Fe}, \state{NM} \postcode{87501}, \country{USA}}}


% Contact information of the corresponding author
%\corr{Correspondence:
%  Richard Golnik, richard@bioinf.uni-leipzig.de; Tel.: +49-341-97-16626}



%\abstract{
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle
\holy{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preliminaries}

A reaction network $(X,R)$ is tuple of two finite sets, set of metabolites $X$ 
and a set of reactions $R$. For any $r\in R$ we can write a stoichiometric equation as:
	\begin{equation}
		\sum_{x\in X}s^-_{xr} \cdot x \rightarrow s^+_{xr}\cdot x
	\end{equation}
where $s^{\pm}_{xr}$ are the educt and product stoichiometry of the molecule $x$ in 
the reaction $r$. The \emph{stoichiometric matrix} $\SM$ encodes all net-stoichiometries:
\begin{equation}
	\SM_{xr}\coloneqq s^+_{xr}-s^-_{xrs}
\end{equation}
 We denote by 
	\begin{equation}
		\begin{split}
			E: R \rightarrow X, E(r) & \coloneqq \{x\in X \ \vert \ s^-_{xr}-s^+_{xr}>0\} \\
			P: R \rightarrow X, P(r) & \coloneqq \{x\in X \ \vert \ s^-_{xr}-s^+_{xr}<0\} \\
		\end{split}
	\end{equation}
the reactants (educts) and products of reaction $r$, respectively. A catalyst is an entity $x\in X$ such 
that $s^{-}_{xr}\cdot s^{+}_{xr}\neq 0$ and we say that $r$ is explicitly catalyzed 
by $x$. In case $s^-_{xr}>s^+_{xr}>0$, $x$ is both reactant and catalyst 
of reaction $r$, while in case $s^+_{xr}>s^-_{xr}>0$, $x$ is both product and catalyst 
of reaction $r$. Note that a reaction may have multiple catalysts. We collect all catalysts 
for a reaction $r$ in the set $\cat_r$ and denote by $\cat(R)\coloneqq\{(K_r,r) \ | \ r\in R 
\text{ explicitly catalyzed}\}$ the set of \emph{catalyzations}. Note that it is possible to have 
$\cat(R)=\emptyset$. The catalysts of a \emph{catalyzation} are denoted by $X(\cat_r)$. The 
triple $(X,R,\cat)$ with $\cat=\cat(R)\neq\emptyset$ is called a partially catalyzed 
RN. If $|\cat| = |R'|$, i.e., each reaction is catalyzed, we call $(X,R,\cat)$ a catalyzed RN. 

A tuple $(X', R')$ is called a subnetwork of $(X,R)$ if $X'\subseteq X, R'\subseteq R$- A 
catalyzed network We say a subnetwork $(X',R')$ is well formed if for any $r\in R': \exists x_1,x_2\in X: 
s^-_{x_1r}>0, s^+_{x_2r}>0$. Considering a subnetwork $(X',R')$, we may distinguish 
a certain subset of entities $F', W'\subseteq X$ defined as
\begin{equation}\label{eq:FoodWaste}
	\begin{split}
		F'&\coloneqq \{x\in X: x\notin X', \exists r\in R': s^{-}_{xr}>0\}\\
		W'&\coloneqq \{x\in X: x\notin X', \exists r\in R': s^{+}_{xr}>0\}.
	\end{split}
\end{equation}
We call $F'$ and $W'$ the set of food and waste molecules for the subnetwork $(X',R')$,
respectively. A subnetwork is called \emph{educt} and \emph{product complete} if $F'\subseteq X'$ and 
$W'\subseteq X'$, respectively. 

A (catalyzed) RN can be represented by its \emph{K\"onig graph}, a directed bipartite graph $\king (X,R,\cat) \coloneqq 
(X\cup R, E_1\cup E_2)$ with
\begin{equation}
	\begin{split}
		E_1 & \coloneqq \{(x,r) \ \vert \ s^-_{xr}>0\} \\
		E_2 & \coloneqq \{(r,x) \ \vert \ s^+_{xr}>0\}.
	\end{split}
\end{equation}

\TODO{Define:,  
\begin{itemize}
	\item{Autocatalytic matrices and autocatalytic cores}
	\item{Child-selections}
	\item{CS-matrices, Metzler-matrices}
	\item{(strong) Metzler column, i.e., no negative entry on the diagonal}
	\item{Fluffles}
	\item{Define CAF}
\end{itemize}
}

%To align with the setting of \cite{hordijk_detecting_2004}, we define a slight variation denoted as \emph{catalyzed 
%K\"onig graph} as the bipartite directed graph $\queen (X,R,\cat) \coloneqq (X\cup R, E_1\cup E_2\cup E_{\cat})$
%
%\begin{equation}
%	\begin{split}
%		E_1 & \coloneqq \{(x,r) \ \vert \ \SM_{xr}<0\} \\
%		E_2 & \coloneqq \{(r,x) \ \vert \ \SM_{xr}>0\} \\
%		E_{\cat} & \coloneqq \{(x,r) \ \vert \ x\in X(\cat_r)\}.
%	\end{split}
%\end{equation}

\section{RAFs}

We adapt the definition of a reflexive autocatalytic food-generated system \cite{hordijk_detecting_2004}, here 
to our notation.
\vspace{6pt}
\begin{definition}[RAF]\label{def:RAF}
	Let $(X,R,\cat)$ be a catalyzed network with $F\subseteq X$. Then
	a set $\RAF\subseteq R$ is called  
		\begin{itemize} 
			\item[i.]{\emph{reflexive autocatalytic} (RA) if $\forall r\in \RAF: \emptyset \neq X(\mathcal{K}_r)\subseteq E(R')\cup P(R')$}
			\item[ii.]{\emph{F-generated} if $E(\RAF)\subseteq \closure{\RAF}{F}$}
			\item[iii.]{\emph{reflexive autocatalytic} and \emph{F-generated} (RAF) if both i. and ii. hold}
		\end{itemize}
\end{definition}
\vspace{6pt}

Note that $ii.$, together with Eq.\ref{eq:Closure}, directly implies that all products for any reaction $r\in \RAF$ are also contained 
in the closure of $F'$, thus $P_r\subseteq \closure{\RAF}{F}$. Special attention will be put on a RAF $R'$ such that there is no 
$\RAF'\subset \RAF$ that is again a RAF. In the literature, this notion has been termed \emph{irreducible} \cite{hordijk_detecting_2004, 
hordijk_autocatalytic_2013, hordijk_autocatalytic_2010}. However, to avoid confusion with the notion of irreducibility of a matrix, 
we refer to such a RAF as a \emph{minimal RAF}. 

Before connecting the notion of a RAF with the definition of an autocatalytic subnetwork, we start by translating specific properties of a RAF 
into the bipartite K\"onig graph. We start with the consequences of the closure. The closure of a set $X'$ w.r.t. to a set $R'$ denoted as $\closure{R'}{X'}$ is the 
unique minimal set $Y$ containing $X'$ such that for any $r\in R': E(r)\subseteq Y \Rightarrow P(r)\subseteq Y$. Thus:

\begin{equation}\label{eq:Closure}
	\closure{R'}{X'} \coloneqq \min \underbrace{\{ Z \subseteq X \ | \ X'\subseteq Z, E(r) \subseteq Z \Rightarrow P(r) \subseteq Z \ \forall r\in R'\}}_{\eqqcolon \mathfrak{C}_{R'}(X')}
\end{equation}

However, it will be convenient to obtain the set $\closure{R'}{X'}$ iteratively. We therefore define:

\begin{equation}
	\cl_{R'}: \mathfrak{P}(X) \rightarrow \mathfrak{P}(X), \cl_{R'}(Z) \coloneqq Z \cup \{P(r) \subseteq Z \ \vert \ E(r)\subseteq Z\}. 
\end{equation}
\vspace{6pt}

We will write $\cl(X')$ instead of $\cl_{R'}(X')$ as well as $\closure{}{X'}$ instead of $\closure{R'}{X'}$ where appropriate. 
It is indeed not obvious that the repetitive iteration of $\cl_{R'}(X')$ yields $\closure{R'}{X'}$. However, 
recall that an RN is composed of two finite-sized sets, i.e., $|X|<\infty$ and $|R|<\infty$. By definition, the composition 
$\cl\circ \cl$ is well defined. Moreover, we let $\cl^n(X')\coloneqq \left(\bigcirc^n_{i=0} \ \cl \right)(X')$, i.e., $\cl^0(X')\coloneqq X'$. 
The intuitive assumption that a repetitive application of $\cl$ on a set $X'$ actually converges is indeed true.

\vspace{6pt}
\begin{lemma}\label{lem:finSize}
	Let $(X,R)$ be a reaction network. For a set $X'\subseteq X$ and $R'\subseteq R$ there 
	is an $n\in \mathbb{N}$ such that: 
	\begin{equation}
		\cl^n(X') = \cl^m (X'), m\geq n, m\in \mathbb{N}
	\end{equation}
\end{lemma}
\begin{proof}
	Assume this is not the case. Then in each $k$-th step 
	\begin{equation}
		|\cl^k(X')| < |\cl^{k+1}(X')|,
	\end{equation}
	which implies that
	\begin{equation}
		|\cl^k(X')| \overset{k\rightarrow\infty}{\longrightarrow}{\infty}	
	\end{equation}
	a contradiction given that $|X|<\infty$.
\end{proof}

The sequence $(\cl^k(X'))_{k\in \mathbb{N}}$ thereby converges, and it remains to show that for the limit it holds
$\lim_{k\rightarrow \infty} \cl^k(X') = \closure{}{X'}$. By definition, for any $k\in\mathbb{N}: \cl^k(X')\subseteq \closure{}{X'}$. 
In addition, the convergence of $\cl^k(X')$ gurantees that $\lim_{k\rightarrow \infty} \cl^k(X')\in \mathfrak{C}(X')$. Thus by 
minimality $\closure{}{X'}\subseteq \lim_{k\rightarrow \infty} \cl^k(X')$, which yields by mutual inclusion that 
$\lim_{k\rightarrow \infty} \cl^k(X') = \closure{}{X'}$. With the uniqueness of the limit, the subsequent corollary follows.

\vspace{6pt}
\begin{corollary}\label{cor:seqLimit}
	Let $(X,R,\cat)$ be a catalyzed network of finite size with $X'\subseteq X, R'\subseteq R$. Then $\closure{R'}{X'}$ 
	is the unique limit of the sequence
	\begin{equation}
		\left(\left(\bigcirc_{i=1}^k \ \cl_{R'}\right)(X')\right)_{k\in\mathbb{N}}.
	\end{equation}
	In addition, there is an $n\in\mathbb{N}: \cl^n_{R'}(X')=\cl^m_{R'}(X'), m\geq n$.
\end{corollary}
\vspace{6pt}
By definition of $\cl_{R'}$, the sequence $(\cl_{R'}^k(X')_{k\in\mathbb{N}}$ directly implies a partial order on the reactions 
that can be carried out in the $k$-th step, i.e., for which all reactants are contained in the set $\cl^k_{R'}(X')$. We thereby 
let:
\begin{equation}
	\PO_{R'}^k(X') \coloneqq \{r\in R' \ | \ E(r)\subseteq \cl^k_{R'}(X')\}
\end{equation}

For both $\cl^k_{R'}(X)$ and $\PO_{R'}^k(X')$, it might be convenient to consider their partial order as:
\begin{equation}
	\begin{split}
		\POX_{R'}^0(X')& \coloneqq X' \qquad \POX_{R'}^k(X')\coloneqq \cl^k_{R'}(X)\setminus \left(\bigcup_{i=0}^{k-1} \cl^k_{R'}(X) \right)\\
		\POR_{R'}^0(X') & \coloneqq \emptyset \qquad \POR_{R'}^k(X')\coloneqq \PO^k_{R'}(X) \left(\bigcup_{i=0}^{k-1} \PO^k_{R'}(X) \right)
	\end{split}
\end{equation}
We are now in the position to deduce the consequences of Def.~\ref{def:RAF}ii. to the bipartite K\"onig representation of a RAF. 
\vspace{6pt}
\begin{lemma}\label{lem:RAFPath}
	Let $(X,R,\cat)$ be a catalyzed network with $F\subseteq X$ and $\RAF$ an RAF. Then, 
	for any $x\in \closure{\RAF}{F}\setminus F: \exists f\in F: P=(f, \ldots, x)$ is a path in 
	$\king'\coloneqq \king(\closure{\RAF}{F}\cup F, R', \cat')$.
\end{lemma}
\begin{proof}
	Let $x\in \closure{\RAF}{F}\setminus F$. By Corollary~\ref{cor:seqLimit} we have for some $n\in\mathbb{N}$ that
	$\closure{\RAF}{F}\setminus F = \cl^n_{\RAF}(F) \setminus F$. Thus, there is the sequence:
	\begin{equation}
		(\mathscr{Z}^k_{\RAF}(F))_{n\in\mathbb{N}}\coloneqq (\cl^{k-1}_{\RAF}(F), \PO^k_{\RAF}(F))_{n\in\mathbb{N}}
	\end{equation}
	such that for any $r\in \PO^k_{\RAF}(F)$ there is $y\in \cl^{k-1}_{\RAF}(F), z\in\cl^{k}_{\RAF}(F): (y,r)\in E_1(\king'), (r,z)\in E_2(\king')$. 
	Thus, starting with $x\in \cl^{n}_{\RAF}(F)$ and recursively applying the upper argument, there is a sequence of vertices $
	(x_0, r_1, x_1, \ldots, r_n, x_n): (x_{i-1},r_i)\in E_1(\king'), (r_i,x_i)\in E_2(\king'), 1\leq i\leq n, x=x_n$ that is a path 
	in $\king'$.
\end{proof}

\section{RAFs and autocatalytic subnetworks}

We continue by connecting the notion of RAFs to autocatalysis sensu Blokhuis \cite{blokhuis_Universal_2020}, which  
provided the widely accepted definition of (structural) autocatalysis in 2020.
\vspace{6pt}
\begin{definition}\label{def:autSubRN}
  An RN $(X,R)$ is \emph{autocatalytic} if it contains a sub-RN $(X',R')$ such that
\begin{enumerate}
 \item[(i)]  $(X',R')$ is  well-formed;
 \item[(ii)]  $\mathbf{S}[X',R']$ is semi-positive.
\end{enumerate}
\end{definition}
\vspace{6pt}

Our first goal will be to find suitable restrictions of RAFs such that we obtain both of these conditions.
Indeed, restricting the set of considered molecules to all but the food molecules yields semipositivity 
of the particular submatrix.
\vspace{6pt}
\begin{lemma}
	Let $(X,R)$ be a catalyzed RN with food-set $F$ and $\RAF$ a RAF. Then it holds that 
	the matrix $A\coloneqq \SM[\closure{\RAF}{F}\setminus F,\RAF]$ is semipositive, i.e., $Av>0$.
\end{lemma}
\begin{proof}
	We prove by induction. We know that for some $n\in \mathbb{N}: \cl^n_{\RAF}(F)=\closure{\RAF}{F}\eqqcolon X'$. 
	We observe that for an $x\in \POX^k\coloneqq \POX^k_{\RAF}(F)$, $\SM_{xr}=0$ for any 
	$r\in \POR^l \coloneqq \POR^l_{\RAF}(F), l<k \ (*)$. We initialize a map: $f: X' \rightarrow \mathbb{R}, f(x)\coloneqq 0$, 
	that will be updated in each step. Thus, we start with the set $\POR^n$. For each an $r\in \POR^n$, we let 
	$v_r\coloneqq 1$, and update for each $x\in X'$:
	\begin{equation}
		f(x) \leftarrow f(x) + \sum_{r\in \POR^n} v_r \cdot \SM_{xr}
	\end{equation}
	then for all $x\in \POX^n: f(x)>0$. 
	
	Assume now that for some $1\leq k\leq n$ it holds that $f(x)>0, \forall x\in \POX^k$. Then, for $k-1$
	we choose an arbitrary ordering of $r\in \POR^{k-1}$, since each $x\in \POX^{k-1}$ can only be 
	a product of reactions in $\POR^{k-1}$ but never be a reactant. We let:
	\begin{equation}
		v_r\coloneqq \left\vert \min_{x\in \POX^{k-1}} \left(\frac{f(x)}{s}\right)\right \vert + 1, s\coloneqq \begin{cases}\SM_{xr} & \text{if } \SM_{xr}\neq 0 \\ 1 & \text{otherwise} \end{cases}
	\end{equation}
	Then we update again for each $x\in X'$:
	\begin{equation}
		f(x) \leftarrow f(x) + \sum_{r\in \POR^n} v_r \cdot \SM_{xr}
	\end{equation}	
	 and obtain again that forall $x\in \POX^{k-1}: f(x)>0$ and with observation $*$ that also $f(x)>0, \in \POX^{\ell}: f(x)>0, k-1\leq \ell \leq n$.
	 Then by construction, we obtain $v_r$ is strictly positive and $Av>0$. 
\end{proof}
\vspace{6pt}

A natural extension to this statement relies in considering not only species from 
$\closure{\RAF}{F}\setminus F$ but from the set of food-generated entities, i.e.
\begin{equation}
	\mathbf{X}_{\RAF} \coloneqq \bigcup_{k=1}^n \POX^k_{\RAF}(F)
\end{equation}

However, in this case, semipositivity is not guaranteed. To see this, consider 
the following example:
\begin{equation}
	\begin{split}
		r_1: f_1 & \overset{f_1}{\longrightarrow} x_1\\
		r_2: x_1 & \overset{x_1}{\longrightarrow} f_1 \\		
	\end{split}
\end{equation}
with the RAF $\RAF\coloneqq \{r_1,r_2\}$ and food-set $F\coloneqq \{f_1\}$. Then
$\SM[\mathbf{X}_{\RAF}, \RAF]$ reads:
\begin{equation}
	\begin{pmatrix}
		-1 & 1 \\
		1 & -1
	\end{pmatrix}
\end{equation}
which is indeed not semipositiv. The semipositivity of $A\coloneqq \SM[(\closure{\RAF}{F}\setminus F,\RAF)]$ 
in general originates from at least one food-generated reaction. For example, in the following RN:
\begin{equation}
	\begin{split}
		r_0: f_1 & \overset{f_2}{\longrightarrow} x_1 \\ 
		r_i: x_i & \overset{x_i}{\longrightarrow} x_{i+1},
	\end{split}
\end{equation}
reaction $r_0$ forms a strong Metzler-column in $A$, which allows for an unrestricted input of $x_1$. \TODO{mhhh...I am not satisfied yet}.
However, $r_0$ has no reactant in $\closure{\RAF}{F}\setminus F$, not even a catalyst. By 
definition~\ref{def:autSubRN}, $(\closure{\RAF}{F}\setminus F,R')$ is not an autocatalytic subnetwork 
since it is not well-formed. One way of avoiding such a situation is to require that none of the 
catalysts is contained in the food set. Consider the following 
RAF $\RAF={r_1,r_2}$, with food-set $F=\{f\}$ and $X\coloneqq \{f,x_1,x_2\}$.
\begin{equation}
	\begin{split}
		r_1&: f  \overset{x_1}{\longrightarrow} x_2 \\ 
		r_2&: x_2  \overset{x_2}{\longrightarrow} x_1
	\end{split}
\end{equation}
The matrix $A\coloneqq \SM[(\closure{\RAF}{F}\setminus F,R')]$ then reads:
\begin{equation}
	A\coloneqq 
		\begin{pmatrix}
			0 & 1\\
			1 & -1
		\end{pmatrix}
\end{equation}
which is an autocatalytic core of size $2$ that is associated with an elementary 
circuit in $\king(\closure{\RAF}{F},R'), R')$. This is, however, no coincidence. 
Let us therefore consider only \emph{catalytically autonomous} RAFs $\RAF$, 
i.e., for which $\cat(\RAF)\cap F=\emptyset$.
\vspace{6pt}
\begin{lemma}
	Let $(X,R)$ be a catalyzed network with food-set $F$ and $\RAF$ a \emph{catalytically autonomous} RAFs. 
	Then $(\closure{\RAF}{F},\RAF)$ contains an autocatalytic core $(X',R')$ that is either an explicit autocatalytic 
	reaction or $\king(X',R')$ is an elementary circuit and the corresponding CS matrix $\SM[\child]$ has at least 
	one strong Metzler column.
\end{lemma}
\begin{proof}
	\TODO{Include and adapt proof from Overleaf}
\end{proof}
\vspace{6pt}

Generalizing this notion, we can require that every reaction has a reactant (not necessarily a net-reactant)
that is not an element of the food set. 

\begin{lemma}
	Let $(X,R)$ be a catalyzed network with food-set $F$ and $\RAF$ a RAF, where for each $r\in R'$ there is
	$x\in \closure{\RAF}{F}\setminus F: s_{xr}^->0$. Then $(\closure{\RAF}{F},\RAF)$ contains an autocatalytic 
	core $(X',R')$ that is either an explicit autocatalytic reaction or $\king(X',R')$ is an elementary circuit and the 
	corresponding CS matrix $\SM[\child]$ has at least one strong Metzler column.
\end{lemma}
\begin{proof}
	
\end{proof}
 
Building on this....

\begin{lemma}
	A RAF is a CAF or it contains an autocatalytic core.
\end{lemma}
\TODO{Another open point here is that we can have food molecules that are produced....not entirely sure yet how to 
deal with this case.}

\vspace{6pt}

\section{RAF-Subnetworks}

In this subsection, we aim to generalize the framework of RAFs to a subnetwork setting.

\subsection{Reflexively autocatalytic subnetworks}

We start with the reflexive-autocatalytic part. We call a subnetwork $(X', R')$ partially catalyzed if $\cat(R')\neq \emptyset$. 
\vspace{6pt}
\begin{definition}
	Let $(X,R)$ be a catalyzed RN. A subnetwork $(X',R')$ is called reflexive-autocatalytic if for each 
	$r\in R': \cat_r\neq \emptyset \ (X(\cat(R')\subseteq X')$. It is called autonomously reflexive-autocatalytic 
	if for each $r\in R': \cat_r\neq \emptyset \ and X(\cat(R')\subseteq X'$.
\end{definition}
\vspace{6pt}
We denote the subgraph of a subnetwork by $\king'\coloneqq \king(X',R')$ and write $\cat'$ instead of $\cat(R')$. A direct consequence 
is the following lemma:
\vspace{6pt}
\begin{lemma}\label{lem:RASubnetwork}
	Let $(X, R, \cat)$ be a catalyzed RN. A subnetwork $(X',R')$ is (autonomously) reflexive-autocatalytic if and only if
	for all $r\in R' \ \exists x\in X: (x,r),(r,x)\in E(\king(X\cup X(\cat'), R') \ (E(\king'))$. 
\end{lemma}
\begin{proof}
	If $(X',R')$ is reflexive autocatalytic $|R'|=|\cat'|$, thus each reaction $r$ is explicitely catalyzed by an $x_r\in X(\cat_r)\subseteq X$.
	Then $s^-_{x_rr}>0$ and $s^+_{x_rr}>0$ yields by definition $(x_r,r)$ and $(x_r,r) \in E(\king(X\cup X(\cat'), R')$, respectively.
	If $(X',R')$ is autonomously reflexive-autocatalytic then $X(\cat'\subseteq X'\Rightarrow \king(X\cup X(\cat'), R') = \king'$ which
	yields the second part of the claim. Conversely, if for each $r\in R': \exists x\in X$ such that $(x,r),(r,x)\in E(\king(X\cup X(\cat')), R')$, 
	then by definition $s^-_{xr}>0,s^+_{xr}>0$, thus $x\in X(\cat_r)$. If, additionally, $(x,r),(r,x) \in E(\king')$ then $x\in X'$ and thus 
	$X(\cat'\subseteq X'$ which yields that $(X',R')$ is autonomously reflexive-autocatalytic. 
\end{proof}
\vspace{6pt}

\subsection{F-generated subnetworks}

In theory, for an RN $(X,R,\cat)$, $F$ could be chosen arbitrarily. Depending on the network structure and the RAF $R'$, 
$F$ might be identical to its own closure. To see this, consider the following example network: 
\begin{equation}
	\begin{split}
		r_1: x_1 \overset{x_1}{\longrightarrow} x_2 \\
		r_2: x_2 \overset{x_2}{\longrightarrow} x_1 \\
	\end{split}
\end{equation}
with $F=\cat=X=\{x_1,x_2\}$ and RAF $\RAF = \{r_1,r_2\}$. Then $F=\closure{\RAF}{F}$. However, $F$ could also contain reactions 
that are not connected to the rest, depending on the RAF. For example
\begin{equation}
	\begin{split}
		r_1: x_1 &\overset{x_1}{\longrightarrow} x_2 \\
		r_2: x_2 &\overset{x_2}{\longrightarrow} x_1 \\
		r_3: x_3 &\overset{x_3}{\longrightarrow} x_1 
	\end{split}
\end{equation}
with $F=\cat=X=\{x_1,x_2,x_3\}$ and RAF $\RAF=\{r_1,r_2\}$, we have $x_3\in F\Rightarrow F\subseteq \closure{\RAF}{F}$ but $x_3$ is disconnected
in the graph $\king(X(\RAF) \cup F, \RAF, \cat(\RAF))$. In contrast, a food-set $F'$ for a subnetwork $(X', R')$ as defined in Eq.~\ref{eq:FoodWaste} is a direct 
consequence from the set of entities $X'$ and the set of reactions $R'$. 

\vspace{6pt}
\begin{definition}[F-generated subnetwork]
	Let $(X, R, \cat)$ be a catalyzed RN. A subnetwork $(X',R')$ is called $F$-generated, if $X'\subseteq \closure{R'}{F}$.
\end{definition}
\vspace{6pt}

An immediate question arising is then how to construct a minimal set $F$ to obtain an $F$-generated subnetwork. Clearly, we have  
that $F'\subseteq F$ if $(X',R')$ is $F$-generated. 
\vspace{6pt}
\begin{lemma}
	Let $(X, R, \cat)$ be a catalyzed RN and $(X',R')$ a subnetwork. If $\king[X'\cup R']$ is a fluffle, then $(X',R')$  
	is an $F$-generated subnetwork for any of the sets $F_x\coloneqq F'\cup\{x\}, x\in X'$.
\end{lemma}
\begin{proof}
	If $\king[X'\cup R']$ is a fluffle, then any reaction has a single reactant in $(X',R')$. In addition, there is a unique CS $\child$ 
	defined by the reactant-to-product edges. For an arbitrary $x'\in X'$ and the set $F'$ we have $E(\kappa(x))\subseteq 
	F_x\coloneqq F'\cup\{x\}$, which yields that $P(\kappa(x))\subseteq \cl_{R'}(F_x)$. For all $y\in P(\kappa(x))$, the same 
	argument applies as well as for all any $z\in \POX^k_{R'}(F), k\leq n$. Since $\king[X'\cup R']$ is a fluffle, it is strongly 
	connected. Thus, for each $r\in R'$ there is path $(x, \kappa(x), \ldots, r)$, and thereby an $k\leq n: r\in \POR_{R'}(F)$. 
	Hence, $X'\subseteq \closure{R'}{F}$.
\end{proof}
\vspace{6pt}
Since irreducible Metzler CS matrices have a bipartite graph representation as a fluffle, 
the following statement is a direct consequence from the former lemma.
\vspace{6pt}
\begin{corollary}
	Let $(X',R')$ be a subnetwork that has an associated autocatalytic, irreducible 
	Metzler CS matrix $\SM[\child]$. Then $(X',R')$ is an $F$-generated
	subnetwork for any $F_x\coloneqq F'\cup \{x\}, x\in X'$.
\end{corollary}
\vspace{6pt}
Any autocatalytic core $(X',R')$ can then be generated by the union of $F'$ and a single species from $X'$. 
\vspace{6pt}
\begin{corollary}
	Let $(X',R')$ be an autocatalytic core. Then $(X',R')$ is an $F$-generated subnetwork for any $F_x\coloneqq F'\cup \{x\}, x\in X'$.
\end{corollary}
\vspace{6pt}
For irreducible non-Metzler matrices, such a result cannot be obtained. In the worst case, 
all but one species might have to be added to $F'$ to obtain an $F$-generated subnetwork. 
To see this, consider the following subnetwork $(X',R')$: 
\begin{equation}
	\begin{split}
		r_1&: x_1 + \epsilon x_3 \rightarrow x_2 \\
		r_2&: x_2 + \epsilon x_1 \rightarrow x_3 \\
		r_3&: x_3 + \epsilon x_2 \rightarrow x_1
	\end{split}
\end{equation}
with corresponding CS matrix:
\begin{equation}
	\SM[\child]=\begin{pmatrix}
				-1 & -\epsilon & 2 \\
				1 & -1 & -\epsilon \\
				-\epsilon & 1 & -1 
			\end{pmatrix}
\end{equation}
which is autocatalytic for epsilon small enough with $v=\begin{pmatrix}5 & 4 & 3\end{pmatrix}^T$. 
In \cite{golnik_enumeration_2025}, it has been shown that any CS matrix with irreducible Metzler has a 
spanning fluffle $\king(\child)$. Although still strongly connected the induced subgraph $\king[\child]$ 
might contain additional reactant-to-reaction edges that are not encoded by the CS-bijection $\kappa$.
However, it is sufficient to add all species with an off-diagonal entry.
\vspace{6pt}
\begin{lemma}
	Let $(X', R')$ be a subnetwork with a non-Metzler CS matrix with irreducible Metzler part. Then $(X',R')$
	is $F$-generated for $F= F' \cup N, N=\{x\in X' | \exists r \neq \kappa(x), \SM^-_{xr}>0\}$.
\end{lemma}
\begin{proof}
	Since $\SM[\child]$ has irreducible Metzler part, $\king(\child)$ is strongly-connected, which implies that
	also $\king[\child]$ is strongly connected. Then for any $x\in N: E(\kappa(x))\in F$, thus $\kappa(x)\in \POR_{R'}(F)$ 
	and $P(\kappa(x))\in \cl_{R'}(F)$. We can now recursively apply this argument to all $y\in P(\kappa(x))$
	and obtain with the strong-connectedness of $\king[\child]$ that $X'\subseteq \closure{R'}(F)$.
\end{proof}
\vspace{6pt}
%\subsection{Reflexively autocatalytic and $F$-generated subnetworks}
%
%We now combine the two definitions above. 
%
%\begin{definition}
%	Let $(X, R, \cat)$ be a catalyzed RN and $(X',R')$ a subnetwork. A reflexive autocatalytic subnetwork $(X',R')$ 
%	is called a RAF-subnetwork if there is a set $Y'\subseteq X'$ such that $(X',R')$ is $F$-generated for $F\coloneqq F'\cup Y'$.
%\end{definition}
%
%A trivial statement that follows directly from the definition is that for any RAF subnetwork

\vspace{6pt}
The definition of the food-set $F'$ in Eq.~\ref{eq:FoodWaste} does not include catalysts. We may additionally define the catalyst 
specific food-set for $(X',R')$ as follows:
\begin{equation}
	F'_{\cat'}\coloneqq \{x\in X(\cat') \ | \ x\notin X'\} 
\end{equation}
}

\vspace{6pt}
\bibliography{RAFCores}

\end{document}
